How to compute the fusion product of MV cycles in type A

### 2021-05-15 draft.tex
last changes

\documentclass[draft]{article}
\usepackage{basic}
\usepackage{emoji}
% TODO: The matrix is lower triangular and the lower-triangular matrix is
% \setemojifont{Apple Color Emoji}
% Working title: 
\title{How to compute the fusion product of MV cycles in type A}
\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
% \date{October 2020}
\date{\today}

@@

The purpose of this paper is to give a conceptually elementary way to compute this product in type $A$. We do not know how fruitful this work might be in the larger landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is as yet computationally expensive. 
% 
Moreover, it is not clear why one should care about the fusion product on bases. \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull}

@@

In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 

@@

    \left[
        \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
            & 1 & & & & & \\
            &  & 1 & & & & \\
        A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
            &  & &  & 1 & & \\
            A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
            A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
            A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
    \end{BMAT}
    \right]\,. 

@@

@@

To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
of polynomials 
% $ g(A) = \left( g(A)_{ij} \right)$ 
$g(A)$
in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
\begin{equation}
    \label{eq:mvyofa}
    g(A)_{ij} = 
\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
        % \text{ if $ i = j$} \\
        - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
    %  \text{ if $ i \ne j$ }
\end{cases}
\end{equation}
where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
For example,
\[
    \left[
        \begin{BMAT}(e){ccc;cc}{ccc;cc} 
        0 & 1 & 0 & 0 & 0\\
        0 & 0 & 1 & 0 & 0\\
        A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
        0 & 0 & 0 & 0 & 1\\
        A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
        \end{BMAT}\right]    
        \mapsto 
        \left[\begin{array}{rr}
            t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
            -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
        \end{array}
        \right]\,. 
\]
% For example, the $A$ above will define 
% \acom{the transpose of! TODO. Had script?}
% \[
% \begin{bmatrix}
%     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
%     & t^2 \\
%     & & t \\
%     & & & t 
% \end{bmatrix}    
% \]
% 
% \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
% \acom{Ok.}
% 
\acom{Can add sentence before making next definition? To the effect of ``In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.''}
\begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
$$
\UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
$$
\end{definition}
So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
For example, elements of $ \UU_{0,s}^{(1,1,0),(2,1,1)}$ look like 
% 
% $\UU_{0,0}^{(?),(?)}$ entries look like 
% \[
%     \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
%         0 & 1 & 0 & 0 & 0\\
%         0 & 0 & 1 & 0 & 0\\
%         0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
%         0 & 0 & 0 & 0 & 1\\
%         0 & 0 & 0 & 0 & 0
%         \end{BMAT}\right]    
%         % \mapsto 
%         % \left[\begin{array}{rr}
%         %     t^{3} & 0 \\
%         %     -A_{12}^2 t - A_{12}^1 & t^{2}
%         % \end{array}\right]
% \]
\[
    \left[
        \begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
        0 & 1 & 0 & 0 & 0 & 0\\
        0 & 0 & 1 & 0 & 0 & 0\\
        0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
        0 & 0 & 0 & 0 & 1 & 0\\
        0 & 0 & 0 & 0 & s & A_{23}^1\\
        0 & 0 & 0 & 0 & 0 & s
        \end{BMAT}
    \right] \,.   
    % \in \UU_{0,s}^{(1,1,0),(2,1,1)}
\]
% 
Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.

@@

The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
% 
\begin{theorem} 
\label{th:TmuWmu}
The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. $$
%\acom{Up to transpose?!}
\end{theorem}
%

@@

Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. 
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$ where $\n\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
\end{corollary}
%The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \textbf{perfect basis} of $\CC[N]$.

@@

The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula 
$$
\begin{aligned}
n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j \\
(i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
(2,2),\dots,(m-1,2),%\\
\dots,%\\
(m-1,m-1)
\end{aligned}
% (i,j) = \begin{smallmatrix}
% \\
% (1,1) \\
% (2,1) & (2,2) \\
% \vdots & & \ddots \\
% (m-1,1) & (m-1,2) & \dots & (m-1,m-1) 
% \end{smallmatrix}
$$
% for 
% $(i,j) = (1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2),\dots,(m-1,m-1)$. 
% 
The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence. See \cite[\S 4]{berenstein1988tensor}.

\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}

\acom{Yes $i = m$ doesn't make sense. Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2,\dots,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things. Right?}

For example, if 
\[
    \tau = \young(1112,23) 
\]
then
\begin{gather*}
%    \text{if } \tau = \young(1112,23) \text{ then } 
\gt(\tau) = \begin{matrix}
       3 \\
       4 & 1 \\ 
       4 & 2 & 0 
   \end{matrix} \text{ and }
   n_\bullet(\tau) = (1,0,1)\,. 
\end{gather*}
% 
%This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
% 
We can associate to $\tau$ an MV cycle. 
%  
\begin{equation*}
    Z(\tau) = 
     \overline{
        \{
            L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
        \}\,. 
     }
\end{equation*}
%

@@

Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$.

@@

On the other hand, by definition 
$$Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}$$

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
\subsection{Fusion of MVCs via BD MVy}
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

>>>>

\documentclass[draft]{amsart}
\usepackage{basic}
\usepackage{emoji}
% TODO: The matrix is lower triangular and the lower-triangular matrix is
% \setemojifont{Apple Color Emoji}
% Working title: 
\title{How to compute the fusion product of MV cycles in type A}
\author{Roger Bai, Anne Dranowski, Joel Kamnitzer} 
% \date{October 2020}
\date{\today}

@@

The purpose of this paper is to give a conceptually elementary way to compute this product in type $A$. We do not know how fruitful this work might be in the larger landscape of geometric representation theory as it is plagued by two major limitations: it does not readily generalize outside of type $A$, and it is as yet computationally expensive. 
% 
Moreover, it is not clear why one should care about the fusion product on bases \emoji{imp} \emoji{grin} \emoji{worried} \emoji{monocle-face} \emoji{skull} except for positivity!

@@

In pictures, and by example, the elements $A$ for 
% $\mu=(3,2,2,1)$ 
$\mu = (1,2,2,3)$ look like 

@@

    TODO: REDO 
    % \left[
    %     \begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
    %         & 1 & & & & & \\
    %         &  & 1 & & & & \\
    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
    %         &  & &  & 1 & & \\
    %         A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
    %         A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
    %         A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
    % \end{BMAT}
    % \right]\,. 

@@

%     \left[\begin{BMAT}(e){c;cc;cc;ccc}{c;cc;cc;ccc} 
%         0 & A_0 & A_1 & A_2 & A_3 & A_4 & A_5 & A_6\\
%         0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
%         0 & 0 & 0 & A_7 & A_8 & A_9 & A_{10} & A_{11}\\
%         0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
%         0 & 0 & 0 & 0 & 0 & A_{12} & A_{13} & A_{14}\\
%         0 & 0 & 0 & 0 & 0 & 0 & 1 & 0\\
%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
%         0 & 0 & 0 & 0 & 0 & 0 & 0 & 0
%         \end{BMAT}\right]

@@

To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
of polynomials 
% $ g(A) = \left( g(A)_{ij} \right)$ 
$g(A)$
in $ M_m(\CC[t]) $ whose $(i,j)$th entry is defined as follows.
\begin{equation}
    \label{eq:mvyofa}
    g(A)_{ij} = 
\begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ij} t^{k-1} & i = j \\
    % A^k_{ji} t^{k-1} & i = j \\
        % \text{ if $ i = j$} \\
        - \sum_{k=1}^{\mu_i} A^k_{ij} t^{k-1} & i \ne j
    %  \text{ if $ i \ne j$ }
\end{cases}
\end{equation}
where 
% $A^k_{ji}$ 
$A^k_{ij}$ is the $k$th entry from the left of the last row of the $\mu_i\times\mu_j$ block of $A$. 
For example,
\[
    % \left[
    %     \begin{BMAT}(e){ccc;cc}{ccc;cc} 
    %     0 & 1 & 0 & 0 & 0\\
    %     0 & 0 & 1 & 0 & 0\\
    %     A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
    %     0 & 0 & 0 & 0 & 1\\
    %     A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
    %     \end{BMAT}\right]    
    %     \mapsto 
    %     \left[\begin{array}{rr}
    %         t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
    %         -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
    %     \end{array}
    %     \right]\,. 
    TODO: REDO
\]
% For example, the $A$ above will define 
% \acom{the transpose of! TODO. Had script?}
% \[
% \begin{bmatrix}
%     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
%     & t^2 \\
%     & & t \\
%     & & & t 
% \end{bmatrix}    
% \]
% 
% \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
% \acom{Ok.}
% 
\acom{Can add sentence before making next definition? To the effect of ``In $\TT_\mu$ we will be interested in a certain family of block upper-triangular matrices.''}
\begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
$$
\UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
$$
\end{definition}
So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
For example, elements of $ \UU_{0,s}^{(1,1,0),(2,1,1)}$ look like 
% 
% $\UU_{0,0}^{(?),(?)}$ entries look like 
% \[
%     \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
%         0 & 1 & 0 & 0 & 0\\
%         0 & 0 & 1 & 0 & 0\\
%         0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
%         0 & 0 & 0 & 0 & 1\\
%         0 & 0 & 0 & 0 & 0
%         \end{BMAT}\right]    
%         % \mapsto 
%         % \left[\begin{array}{rr}
%         %     t^{3} & 0 \\
%         %     -A_{12}^2 t - A_{12}^1 & t^{2}
%         % \end{array}\right]
% \]
\[
    % \left[
    %     \begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
    %     0 & 1 & 0 & 0 & 0 & 0\\
    %     0 & 0 & 1 & 0 & 0 & 0\\
    %     0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
    %     0 & 0 & 0 & 0 & 1 & 0\\
    %     0 & 0 & 0 & 0 & s & A_{23}^1\\
    %     0 & 0 & 0 & 0 & 0 & s
    %     \end{BMAT}
    % \right] \,.   
TODO: REDO
\]
% 
Note that the fibre $  \UU^{\mu', \mu''}_{0,0}$ is the same as the intersection of $ \TT_\mu $ with the set of strictly upper-triangular matrices.

@@

The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
% 
\begin{theorem} 
\label{th:TmuWmu}
The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
$$ 
TODO
% L \mapsto [t|_{\CC[t]^m/L} ]^{\tr}_{\beta_\mu} \,. 
$$
%\acom{Up to transpose?!}
\end{theorem}
%

@@

Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. 
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n_+ \cong\overline\Gr^\lambda\cap S^\mu_+$ where $\n_+\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
\end{corollary}
%The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \textbf{perfect basis} of $\CC[N]$.

@@

The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula 
$$
\begin{aligned}
n_\bullet(\tau)_{i,j} &= \lambda(i+1)_j - \lambda(i)_j \\
(i,j) &=  (1,1),(2,1),\dots,(m-1,1),%\\
(2,2),\dots,(m-1,2),%\\
\dots,%\\
(m-1,m-1)
\end{aligned}
% (i,j) = \begin{smallmatrix}
% \\
% (1,1) \\
% (2,1) & (2,2) \\
% \vdots & & \ddots \\
% (m-1,1) & (m-1,2) & \dots & (m-1,m-1) 
% \end{smallmatrix}
$$
% for 
% $(i,j) = (1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2),\dots,(m-1,m-1)$. 
% 
The pattern $\gt(\tau)$ is recorded as a lower-triangular matrix (the array of shapes of subtableaux $\tau(i)$) and the datum $n_\bullet(\tau)$ is recorded as a sequence. See \cite[\S 4]{berenstein1988tensor}. Below is an example.

% \jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}

% \acom{Yes $i = m$ doesn't make sense. Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),\dots,(m-1,1),(2,2),\dots,(m-1,2,\dots,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things. Right?}

% \begin{example}
    \[
        \tau = \young(1112,23) \qquad \gt(\tau) = \begin{matrix}
            3 \\
            4 & 1 \\ 
            4 & 2 & 0 
        \end{matrix} \qquad n_\bullet(\tau) = (1,0,1) %\,. 
    \]
% \end{example}
% For example, if 
% \[
%     \tau = \young(1112,23) 
% \]
% then
% \begin{gather*}
% %    \text{if } \tau = \young(1112,23) \text{ then } 
% \gt(\tau) = \begin{matrix}
%        3 \\
%        4 & 1 \\ 
%        4 & 2 & 0 
%    \end{matrix} \text{ and }
%    n_\bullet(\tau) = (1,0,1)\,. 
% \end{gather*}
% 
%This combinatorics is relevant because by work of the third author the MV cycles are parametrized by Lusztig data. (This holds much more generally than the present scope.)
% 
We can associate to $\tau$ the MV cycle $Z(\tau)=\overline{\mathring Z(\tau)}$ where
%  
\begin{equation*}
    \mathring Z(\tau) = 
    %  \overline{
        \{
            L\in S^\mu : L\cap\cO^i\in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
        \} \,. 
    %  }
\end{equation*}
%

@@

Recall that $ S^\mu = N_-(\cK) t^\mu$.  For the purposes of this proof, we also introduce the notation $S^\mu_+ := N(\cK)t^\mu$. \acom{Sort out notation, do we no longer need $S_-, N_-$?}

@@

On the other hand, by definition 
$$
Z(\tau)_2 \subset \{ L \in S^\mu : L \in \Gr^{\lambda(i)} \text{ for } i = 1, \dots, m\}\,.
$$

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
\subsection{Fusion of MVCs via BD MVy}
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors of $\CC^N$. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. \acom{We could also use a more compact notation like $A_{(p)}$}
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
% 
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
and
% 
\begin{equation*}
    X(\tau')\ast_{\CC^\times} X(\tau'') = 
    \left\{
        (A,s)\in M_N(\CC) \times \CC^\times: 
        A \in X(\tau') \ast_s X(\tau'') 
    \right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}
